---
title: "kinvicalc workflows"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{kinvicalc workflows}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This vignette walks through the package workflow end to end: register a viscometer,
calculate a kinematic viscosity result, and render the report that a lab operator
would review.

The examples use a temporary registry so the vignette builds the same way in a
clean package check and in an interactive session.

```{r setup, include = FALSE}
options(kinvicalc.reference_db_path = tempfile("kinvicalc-vignette-", fileext = ".db"))
library(kinvicalc)
```

## Register a viscometer

Before any calculation can run, the registry needs a viscometer record with a
calibrated constant for each temperature used by the workflow.

```{r register-viscometer}
viscometer <- tibble::tibble(
  viscometer_id = "001-00001",
  viscometer_size = 1,
  serial_number = "00001",
  calibration_date = as.Date("2024-01-01"),
  status = "active",
  factor_40_top = 0.025,
  factor_40_bottom = 0.029,
  factor_100_top = 0.016,
  factor_100_bottom = 0.018
)

add_viscometer(viscometer)
```

The inserted record is returned from the registry, which makes it easy to confirm
that the identifier, factors, and status were stored as expected.

## Calculate a sample result

A sample result uses two flow-time measurements from the same viscometer. The
package resolves the calibration factor at the analysis temperature, calculates
each determination, and checks whether the pair satisfies the determinability
criterion.

```{r calculate-result}
result <- build_sample_result(
  viscometer_id = "001-00001",
  sample_type = "base_oil",
  analysis_temperature_c = 40,
  time_1 = 200,
  time_2 = 210
)

result
```

This example produces a passed result with a single reported viscosity and a
shared determinability limit. If either flow time is below the method minimum,
the result is still returned but is flagged for review.

## Render a report

The report helpers format the calculation for a lab record or client-facing
summary. In an interactive session, `render_primary_report()` opens the HTML
output directly.

```{r render-report, eval = FALSE}
render_primary_report(result)
```

The same workflow is used in scripts, tests, and the Shiny app, so keeping this
example current is a good check that the package API still fits the intended
workflow.

## Summary

`kinvicalc` centers the workflow around a local viscometer registry, a pair of
flow-time measurements, and a reportable result object. If this vignette builds
successfully, the main package path is working end to end.
