---
title: "kinvicalc workflows"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{kinvicalc workflows}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This vignette walks through the package workflow end to end: register a viscometer,
calculate a kinematic viscosity result, and render the report that a lab operator
would review.

The examples use a temporary registry so the vignette builds the same way in a
clean package check and in an interactive session.

```{r setup, include = FALSE}
options(kinvicalc.reference_db_path = tempfile("kinvicalc-vignette-", fileext = ".db"))
library(kinvicalc)
```

## Register a viscometer

Before any calculation can run, the registry needs a viscometer record with a
calibrated constant for each temperature used by the workflow.

```{r register-viscometer}
viscometer <- tibble::tibble(
  viscometer_id = "001-00001",
  viscometer_size = 1,
  serial_number = "00001",
  calibration_date = as.Date("2024-01-01"),
  status = "active",
  factor_40_top = 0.025,
  factor_40_bottom = 0.029,
  factor_100_top = 0.016,
  factor_100_bottom = 0.018
)

add_viscometer(viscometer)
```

The inserted record is returned from the registry, which makes it easy to confirm
that the identifier, factors, and status were stored as expected.

## Correct a viscometer's calibration factors

If a viscometer's factors were entered incorrectly, `update_viscometer_factors()`
corrects them in place without disturbing the record's identifier, creation
date, use counters, or archive status.

```{r update-viscometer}
update_viscometer_factors(
  "001-00001",
  factor_40_top = 0.0251,
  factor_40_bottom = 0.0291,
  factor_100_top = 0.0161,
  factor_100_bottom = 0.0181,
  updated_by = "jsmith"
)
```

If `notes` is left unspecified (or blank), the update is recorded automatically
as `"Updated <date> by <updated_by>"` so the correction stays traceable; pass an
explicit `notes` value to record a different reason instead. In the Shiny app
(`R/app.R`), entering a viscometer size and serial number that already exist in
the registry changes the "Add to registry" button to "Update Viscometer
Factors" and prompts for confirmation before applying the change, calling this
same function under the hood.

## Calculate a sample result

A sample result uses two flow-time measurements from the same viscometer. The
package resolves the calibration factor at the analysis temperature, calculates
each determination, and checks whether the pair satisfies the determinability
criterion.

```{r calculate-result}
result <- build_sample_result(
  viscometer_id = "001-00001",
  sample_type = "base_oil",
  analysis_temperature_c = 40,
  time_1 = 200,
  time_2 = 210
)

result
```

This example produces a passed result with a single reported viscosity and a
shared determinability limit. If either flow time is below the method minimum,
the result is still returned but is flagged for review.

## Render a report

The report helpers format the calculation for a lab record or client-facing
summary. In an interactive session, `render_primary_report()` opens the HTML
output directly.

```{r render-report, eval = FALSE}
render_primary_report(result)
```

The same workflow is used in scripts, tests, and the Shiny app, so keeping this
example current is a good check that the package API still fits the intended
workflow.

## Summary

`kinvicalc` centers the workflow around a local viscometer registry, a pair of
flow-time measurements, and a reportable result object. If this vignette builds
successfully, the main package path is working end to end.
